---
title: "Die Presse Case Study for Data Engineer"
author: "Jaroslav Kotrba"
date: "March 28, 2022"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: show
    number_sections: true
---
Solution of my case study consists of a Python script to retrieve and transform the data, a SQL script for creation of the "twitter" database and this page to present the result of the analysis.

All scripts and data can be found under:
https://github.com/JaroslavKotrba/TwitterDiePresse

# Connect to database "twitter"
```{r message=F, warning=F}
# install.packages("RMySQL")
library(RMySQL)
mydb = dbConnect(MySQL(), user='Jaroslav_Kotrba', password='milites', dbname='twitter', host='localhost')
dbListTables(mydb)

# name
rs = dbSendQuery(mydb, "select * from name;")
name = fetch(rs, n = -1)
dbClearResult(rs)

# tweet
rs = dbSendQuery(mydb, "select * from tweet")
tweet = fetch(rs, n = -1)
dbClearResult(rs)

# length
rs = dbSendQuery(mydb, "select * from length")
length = fetch(rs, n = -1)
dbClearResult(rs)

# frequency
rs = dbSendQuery(mydb, "select * from frequency")
frequency = fetch(rs, n = -1)
dbClearResult(rs)
```

# Summary data

```{r message=F, warning=F}
# install.packages("tidyverse")
library(tidyverse)
data <- name %>%
    left_join(tweet, by='ID') %>%
    left_join(length, by='ID')

# Summary data
summary(subset(data, select = c(NAME, TWEET, LENGTH)))
```

# TOP ten most active users

```{r message=F, warning=F}
library(tidyverse)
NAME_groupby <- data.frame(data %>% group_by(NAME) %>% 
                            summarise(
                              LENGTH_of_tweet_average = mean(LENGTH),
                              freq = n()
                            ))
head(NAME_groupby[order(-NAME_groupby$freq),],10)
```

```{r message=F, warning=F}
viz <- head(NAME_groupby[order(-NAME_groupby$freq),],10)
# install.packages("ggplot2")
library(ggplot2)
plot <- ggplot(viz, aes(x = freq, y = reorder(NAME, freq))) +
  geom_col(stat='identity', color="cornflowerblue", fill="white") +
  geom_text(aes(label=freq), vjust=0.5, hjust=1.8, color="cornflowerblue", size=3.5) +
  ylab('NAME') +
  xlab('COUNT') +
  theme_bw()
plot
```

# TOP ten longest tweets

```{r message=F, warning=F}
head(data[order(-data$LENGTH),],10)
```

# Summary words

```{r message=F, warning=F}
words <- frequency
summary(subset(words, select = c(WORD, COUNT)))
```

# TOP ten words

```{r message=F, warning=F}
head(subset(words, select = c(WORD, COUNT))[order(-words$COUNT),],10)
```

```{r message=F, warning=F}
viz <- head(subset(words, select = c(WORD, COUNT))[order(-words$COUNT),],10)
# install.packages("ggplot2")
library(ggplot2)
plot <- ggplot(viz, aes(x = COUNT, y = reorder(WORD, COUNT))) +
  geom_col(stat='identity', color="cornflowerblue", fill="white") +
  geom_text(aes(label=COUNT), vjust=0.5, hjust=1.25, color="cornflowerblue", size=3.5) +
  ylab('WORD') +
  theme_bw()
plot
```

# Words associated with "Pandemic"

```{r message=F, warning=F}
# install.packages("wordcloud2")
library(wordcloud2)
viz <- head(subset(words, select = c(WORD, COUNT)), 1000)
wordcloud2(data=viz, size = 4, color='random-dark', backgroundColor = "White")
```

Created by: Jaroslav Kotrba \
https://jaroslavkotrba.com